### 2022-09-20 main/chapter_context.tex
write some on design

\begin{singlespacing}
\section{The \atlas\ Experiment}
%
\begin{epigraphs}
\qitem{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future --- would be interesting if NASA
made a telescope for that%
}%
{Ken~M,
\textit{Comment: Yahoo! News},
2012~\cite{kenm2012inner}}
\end{epigraphs}
\end{singlespacing}

Towards explaining the main result of this thesis,
a search for effects from supersymmetric models in
\atlas~\cite{atlas2022searches},
we first some relevant facts about the \atlas\ detector itself.

\atlas\ is a Titan.
On the \cern\ Large Hadron Collider (LHC), \atlas\ is the largest detector
experiment, and alongside its majors neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A slice of \atlas' design
]{%
A slice of \atlas' design, reproduced from~\cite{atlas1999design1},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}

>>>>

\begin{singlespacing}
\section{The \atlas\ Experiment}
%
\begin{epigraphs}
\qitem{%
if observing outer space gives us a view of the past, observing inner space
would surely give us a glimpse into the future - would be interesting if NASA
made a telescope for that%
}%
{Ken~M,
\textit{Comment: Yahoo! News},
2012~\cite{kenm2012inner}}
\end{epigraphs}
\end{singlespacing}

Towards explaining the main result of this thesis,
a search for effects from supersymmetric models in
\atlas~\cite{atlas2022searches},
we first some relevant facts about the \atlas\ detector ---
its design and history.

The \atlas\ detector did not assemble itself into a preordained form.
It results from a large collaborative effort towards a design that would
provide maximally useful and novel data
without exceeding real-world budgets in construction or operation.
Original designs hoped to construct an \atlas\ detector that could
observe the Higgs boson (which was predicted but yet unseen),
precisely measure known massive objects ($W^\pm$, $Z$, $t$, $b$),
and possibly discover new particles such as those hypothesized by
supersymmetric models~\cite{atlas1999design1}.
We reviews those three goals here.

\paragraph{Higgs boson discovery.}
Prior to \atlas' construction, the Higgs boson mass (and existence) was
poorly known, but loosely constrained by results like
$m_H \gtrsim 90\,\eV[G]$ from direct searches at the
Large Electron–Positron Collider (LEP),
$m_H = 76^{+85}_{-47}\,\eV[G]$ from other data on the electroweak sector,
and $m_H \lesssim 1\,\eV[T]$ from theoretical unitarity arguments~\cite{
atlas1999design2,
ghinculov1998perturb,
lep1999ewk
}.

\paragraph{Precise measurements of known objects.}

\paragraph{Supersymmetry discovery.}
This is not a failure. It is a success.

\paragraph{Design.}
Atlas is a Titan.
On the \cern\ Large Hadron Collider (LHC), \atlas\ is the largest detector
experiment, and alongside its majors neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A central slice of \atlas' design
]{%
A central slice of \atlas' design, reproduced from~\cite{atlas1999design1},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}

### 2022-09-20 main/chapter_searches.tex
write some on design

Early variants of $\cls$ derived it from an identity with posterior tail
probabilities in Poisson and Gaussian special cases~\cite{
Helene1983upper,
pdg1988,
read2000modified,
pdg2022ynf
}
with a contrived frequentist interpretation~\cite{zech1988cls}.
For use in general cases, it is more recently described as a
``modified frequentist'',
``approximate confidence in the signal-only hypothesis''~\cite{
read2000modified,
Read2002cls
}.
High-profile usage in combined Higgs boson searches at the
Large Electron–Positron Collider~\cite{
read1997optimal,
bock1998lower,
etde1998prospects,
junk1999confidence,
lep2000searches,
lep2003search
}
appears to have propelled $\cls$ to prominence;
these early applications used data deficits to exclude their
background-plus signal models, sometimes with the test statistic $t(n) = -n$,
and disliked how deficits led to small \pvalues\ for the background-only model,
with which they might have confusingly set negative limits on the Higgs boson
signal cross-section.
Such \pvalues\ are illustrated in Figure~\ref{fig:searches_sb_n} (left)
for small data counts;
in contrast, $\cls$ can only favour the background-only model, due to its
negative values that are shown on the right of the same figure.

>>>>

Early variants of $\cls$ derived it from an identity with posterior tail
probabilities in Poisson and Gaussian special cases~\cite{
Helene1983upper,
pdg1988,
read2000modified,
pdg2022ynf
}
with a contrived frequentist interpretation~\cite{zech1988cls}.
For use in general cases, it is more recently described as a
``modified frequentist'',
``approximate confidence in the signal-only hypothesis''~\cite{
read2000modified,
Read2002cls
}.
High-profile usage in combined Higgs boson searches at LEP~\cite{
read1997optimal,
bock1998lower,
etde1998prospects,
junk1999confidence,
lep2000searches,
lep2003search
}
appears to have propelled $\cls$ to prominence;
these early applications used data deficits to exclude their
background-plus signal models, sometimes with the test statistic $t(n) = -n$,
and disliked how deficits led to small \pvalues\ for the background-only model,
with which they might have confusingly set negative limits on the Higgs boson
signal cross-section.
Such \pvalues\ are illustrated in Figure~\ref{fig:searches_sb_n} (left)
for small data counts;
in contrast, $\cls$ can only favour the background-only model, due to its
negative values that are shown on the right of the same figure.
